A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-16 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\uline{\textit{Ablation Study: One Branch Attack} To evaluate the impact of $p$ and $\delta$, we add the ablation study on only adding perturbations on the template images or the search regions. The result is shown in Table \ref{table:one_branch}. Experiment results shows that only adding the perturbation to one branch is not useful.
% 对比无目标攻击性能。
For the untargeted attack, only attacking the template/search branch leads to the AO of 0.510/0.714, while attacking both branches leads to the AO of 0.153, which is more effective.
% 有目标
For the targeted attack, only attacking the templat/search branch leads to the AO of 0.156/0.160, while attacking both branches leads to the AO of 0.840. Experimental results show that attacking two branches can achieve better results than attacking one branch.}

\begin{table}[]
  \renewcommand\thetable{XI}
  \centering
  \caption{Attack performance when only use the template/search perturbation.}
  \label{table:one_branch}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
                & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                & AO                & SR                & AO               & SR               \\ \midrule
  Only Template & 0.510             & 0.567             & 0.156            & 0.106            \\
  Only Search   & 0.714             & 0.841             & 0.160            & 0.132            \\
  Both          & 0.153             & 0.123             & 0.840            & 0.890            \\
  \bottomrule
  \end{tabular}
\end{table}

%%%% 问题 2.4 %%%%
\textit{4. As reviewer 1 and reviewer 2 say, the perturbations added to template regions and research regions are not imperceptible, which may be helpful to misguide the tracker. The reviewer considers that adding a similar random pattern on the template and search regions to further illustrate the effectiveness of the proposed method.}

\textbf{To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions. 
% 我们使用高斯噪声代替训练好的扰动来攻击SiamFC++\_GoogleNet。我们在GOT-Val上进行实验。
Specifically, we replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.
% 实验结果的分析
As shown in Table \ref{table:noise}, Gaussian noise cannot effectively attack the tracker even if the standard deviation is up to 100.
For your convenience in cross-checking, the new text is given as follows.
}

% \begin{table}[t]
%   \renewcommand\thetable{XII}
%   \centering
%   \caption{Attack performance using the gaussian random noise. We replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.}
%   \begin{tabular}{@{}rccccc@{}}
%   \toprule
%   \multirow{2}{*}[-2pt]{std} & \multirow{2}{*}[-2pt]{SSIM}& \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
%                              &                            & AO                & SR                & AO               & SR               \\ \midrule
%   1.0                        & 0.98                       & 0.760             & 0.896             & 0.142            & 0.101            \\
%   10.0                       & 0.38                       & 0.761             & 0.898             & 0.143            & 0.102            \\
%   100.0                      & 0.01                       & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
%   \end{tabular}
%   \label{table:noise}
% \end{table}

\begin{table}[t]
  \renewcommand\thetable{XII}
  \centering
  \caption{Attack performance using the gaussian random noise. We replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{std} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                             & AO                & SR                & AO               & SR               \\ \midrule
  1.0                        & 0.760             & 0.896             & 0.142            & 0.101            \\
  10.0                       & 0.761             & 0.898             & 0.143            & 0.102            \\
  100.0                      & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
  \end{tabular}
  \label{table:noise}
\end{table}

\uline{\textit{Ablation Study: Attack performance of the random noise} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions. 
% 我们使用高斯噪声代替训练好的扰动来攻击SiamFC++\_GoogleNet。我们在GOT-Val上进行实验。
Specifically, we replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.
% 实验结果的分析
As shown in Table \ref{table:noise}, Gaussian noise cannot effectively attack the tracker even if the standard deviation is up to 100.
}

### 2021-09-16 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
写response

\begin{table}[t]
  \centering
  \caption{Attack performance using the gaussian random noises. The mean value is set to zero. The standard deviation (std) is changed from 0.1 to 100.0. The noises are added to both the template and the search image, position and size is the same of original setting. The experiment is performed on GOT-Val.}
  \begin{tabular}{@{}rccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{std} & \multirow{2}{*}[-2pt]{SSIM}& \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                             &                            & AO                & SR                & AO               & SR               \\ \midrule
  1.0                        & 0.98                       & 0.760             & 0.896             & 0.142            & 0.101            \\
  10.0                       & 0.38                       & 0.761             & 0.898             & 0.143            & 0.102            \\
  100.0                      & 0.01                       & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
  \end{tabular}
  \label{table:noise}
\end{table}
\uline{\textit{Ablation Study: Attack performance of the random noises} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image. Attack performance using the gaussian random noises. The mean value is set to zero. The noises are added to both the template and the search image, position and size is the same of original setting. We not train.
% 实验结果的分析
As shown in Table \ref{table:noise}, if we add small or midiam noises, it will not the tracking performance. Only very large pattern will have affact, but the SSIM is evry small.
}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.3\textwidth]{images_imperceptible/1.pdf}
  \caption{\uline{Visualization of the perturbations.
  % 介绍什么是 RGB Attack
  Figure (a) demonstrates the pereturbations trained by the RGB attack method, i.e., the attack attack method proposed in Section III.
  % 介绍什么是 YCbCr Attack
  Figure (b) demonstrates the perturbations trained by the YCbCr attack represents the attack method: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. 
  For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
  The perturbed template and search images are then converted into RGB color scpace and fed into the tracking network.
  The other steps of the training process are the same as the attack method in Section III.
  the YCbCr attack method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.}
  }
  \label{fig:YCbCr}
\end{figure}

>>>>

\begin{table}[t]
  \centering
  \caption{Attack performance using the gaussian random noises. The mean value is set to zero. The standard deviation (std) is changed from 0.1 to 100.0. The noises are added to both the template and the search image, position and size is the same of original setting. The experiment is performed on GOT-Val.}
  \begin{tabular}{@{}rccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{std} & \multirow{2}{*}[-2pt]{SSIM}& \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                             &                            & AO                & SR                & AO               & SR               \\ \midrule
  1.0                        & 0.98                       & 0.760             & 0.896             & 0.142            & 0.101            \\
  10.0                       & 0.38                       & 0.761             & 0.898             & 0.143            & 0.102            \\
  100.0                      & 0.01                       & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
  \end{tabular}
  \label{table:noise}
\end{table}
\uline{\textit{Ablation Study: Attack performance of the random noise} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions. 
% 我们使用高斯噪声代替训练好的扰动来攻击SiamFC++\_GoogleNet。我们在GOT-Val上进行实验。
Specifically, we replace the trained perturbations with the gaussion random noise to attack SiamFC++\_GoogleNet. The mean value of the random noise is 0. The standard deviation is changed from 1.0 to 100.0. The experiment is performed on GOT-Val.
% 实验结果的分析
As shown in Table \ref{table:noise}, Gaussian noise cannot effectively attack the tracker even if the standard deviation is up to 100.
}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.48\textwidth]{images_imperceptible/1.pdf}
  \caption{\uline{Visualization of the perturbations.
  % 介绍什么是 RGB Attack
  Figure (a) demonstrates the pereturbations trained by the RGB attack method, i.e., the attack attack method proposed in Section III.
  % 介绍什么是 YCbCr Attack
  Figure (b) demonstrates the perturbations trained by the YCbCr attack represents the attack method: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. 
  For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels.
  The perturbed template and search images are then converted into RGB color scpace and fed into the tracking network.
  The other steps of the training process are the same as the attack method in Section III.
  the YCbCr attack method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.}
  }
  \label{fig:YCbCr}
\end{figure}
